---
title: "Notebook: FUH Validation"
subtitle: Data Workflows and Methodology
author: John Ryan Kivela, MA
output: 
  html_notebook:
    code_folding: hide
    theme: cerulean
    number_sections: yes
    toc: yes
    toc_float: yes
    toc_depth: 3
    toc_collapsed: false
---

# Introduction

## Purpose

The purpose of this notebook is to...

This notebook is the primary source for scripts.

# Overview


# Method

***Data Mining using CRISP-DM***

The CRISP-DM process for data mining was used for this project.

## Business Understanding

### Clear Understanding of business objective


### Success Criteria


### Situation Assessment


### Translate to analytical objectives (Determine Project Goals)


### Clearly understand how action can be taken based on outcomes


### Identify the Business Problem


## Data Understanding


### Identify data sources


### What are the formats?


### Key fieldnames and targets


## Data quality


## Data Preparation

### r Setup

The following setup, libraries, and packages were loaded.

```{r setup, include=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
# Set up knitting options for markdown file
knitr::opts_chunk$set(echo = TRUE)

# Set number of digits to display exponential numbers
options(scipen = 999, 
        show.signif.stars = TRUE)

# Load Packages and libraries
library(tidyverse)
library(readxl)

```

### Data 1

The following SQL query was executed:

```{sql SQL_GlobalMembers, echo=TRUE, eval=FALSE, message=FALSE, warning=FALSE, include=TRUE}

```

The resulting solution is saved as a CSV here:


The raw data files are loaded as indicated below
```{r Data_Load1, ECHO=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Load data

```

### Data 2

### Reference Objects

Several reference objects and data frames were created to provide parameters for determining active membership.

```{r Objects_ForAll, ECHO=TRUE, message=FALSE, warning=FALSE}
# Create common objects for all

```

## Modeling


### Select Modeling Techniques


### Generate Test Design


### Build Model


### Assess Model


## Evaluation


### Eval 1


### Eval 2


### Eval 3
